Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-08-12 supplement.tex
point to validations in supplement
intuition

>>>>

To understand the relationship between model specification and demographic inference, 
consider the five toy models shown on Figure \ref{fig:toymodels}: A) clean split 100ka, 
B) clean split 200ka, C) population growth at 200ka followed by split 100ka, 
D) split 200ka followed by migration until 100ka, and E) split 200ka followed by 
merger 105ka and a new split 100ka.

Models C), D), and E) show qualitatively similar patterns of coalescence rate. 
Given the same data, an IM model (such as D) will infer a potentially much 
deeper population divergence than growth model C and reticulation model E.
